Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-01 sections/theoretical.tex
Adding the figure showing the geometry of the eclipse
I'd like to re-make this later on, to match the linewidth and style
of the rest of the document, but for now it will do.
Took some info from the Conclusion and put it here in a better format. I think that we should move the Stellarium info around, but I will wait for input before acting.

The resulting theoretical lightcurve is shown in Figure \ref{fig:livestream_stellarium_comparison}, alongside the eclipse obscruation derived from the UCA Observatory livestream.
The agreement between the two is excellent, validating our optical eclipse lightcurve.

@@

In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a theoretical lightcurve where the radius of the sun has been changed.

To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System. Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.

@@

Our best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.

>>>>

The resulting theoretical lightcurve is shown in Figure \ref{fig:livestream_stellarium_comparison}, alongside the eclipse obscuration derived from the UCA Observatory livestream.
The agreement between the two is excellent, validating our optical eclipse lightcurve.
% This figure should include the Livestream, Light Sensor, and Stellarium data.

@@

In order to determine the apparent radius of the sun at \unit[1420]{MHz}, we can compare our observed radio lightcurve to a theoretical lightcurve where the radius of the sun has been changed.
To accomplish this, we first downloaded high-accuracy ephemeris data from the JPL Horizons On-Line Ephemeris System. 
Using the angular radii of both the sun and moon along with the angular separation between the two, we calculated the obscured area of the solar disk at 2000 points in time during the eclipse using the geometric relationships shown in Figure \ref{fig:eclipse_geometry}.
These relationships are also given by Equations 1 through 4.

\begin{figure}
  \includegraphics[width=0.5\textwidth]{figures/drawing}
  \caption{\label{fig:eclipse_geometry} The geometric relationships used to calculate the obscuration of the sun.}
\end{figure}

@@

Using these relationships, we can create theoretical lightcurves for varying solar radii.
We calculated the obscured area of the solar disk at 2000 points in time during the eclipse.
Our data found that the radio lightcurve reached a minimum of 30.9\% of the total solar flux during totality, whereas the optical lightcurve reached 0\%.
Assuming a uniform disk brightness, we created theoretical lightcurves for solar radii ranging from $R = 1.0 R_{\odot}$ to $R = 1.5 R_{\odot}$.
These theoretical lightcurves, shown in Figure \ref{fig:TheoreticalVsRadio}, helped us match the dip in relative difference in brightness within the radio lightcurve.
Our model does not take into acount the true non-uniformity of the solar surface, nor does it account for limb darkening.
We found that the best-fit curve has an apparent solar radius of $R_{\mathrm{1420}} = 1.27 R_{\odot}$.
